Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs

### 2017-09-07 redaction/Presentations/DEGIT_Conference/slides_DEGIT_v1.tex

\begin{figure}[htbp]
%\caption{Transport costs (with and without composition effects)}
%\label{fig:totalTC_compeffects_excl}
\begin{center}
\includegraphics[height=7cm]
{graph_composition_all.pdf}
\end{center}
\end{figure}
\hyperlink{slide_compeffects_results}{\beamergotobutton{Back to slide}}
\end{frame}

@@

\begin{frame}
%\frametitle{Composition effects: Comparing with Hummels (2007) (cont')}
Five differences with our method  \vspace{0.1cm}
\footnotesize
\begin{enumerate}

\item Hummels (2007) obtains the fitted ad-valorem rate in one step (the LHS is the observed price gap) while we use a 2-step approach (extract the fitted TC from the \textit{estimated} unfitted ad-valorem rate) - but a slight difference \vspace{0.1cm}
\item Hummels (2007) does not purge its measure of the fitted ad-valorem rate by the country-sector fixed effect  - but only a scale effect \vspace{0.1cm}
\item We separate the country-product fixed effects in two components (country / product), due to the number of fixed effects to estimate in the non-linear setting - robustness analysis to this point (in progress) \vspace{0.1cm}
\item We differ in the weighting scheme to obtain the yearly value of the fitted TC measure.  \vspace{0.1cm}
\begin{itemize}
\footnotesize
\item[-] Hummels (2007): The unweighed average value over the $i,k$ dimension \vspace{0.1cm}
\item[$\neq$] We weight each flow by its relative value in total trade flows observed in 1974 \vspace{0.1cm}
\item[-] Not much of a difference provided the weighting scheme in value is constant over time \vspace{0.1cm}
\item[-] Robustness to the alternative weighting scheme (apply Hummels's (2007) method) in progress
\end{itemize}

@@

>>>>

\begin{figure}[htbp]
%\caption{Transport costs (with and without composition effects)}
%\label{fig:totalTC_compeffects_excl}
\begin{center}
\includegraphics[height=7cm]
{graph_composition_all.pdf}
\end{center}
\end{figure}
\hyperlink{slide_compeffects_results}{\beamergotobutton{Back to slide}} \hyperlink{app_compeffects_Hummels_rob}{\beamergotobutton{Robustness check}}
\end{frame}

@@

\begin{frame}[label = app_compeffects_Hummels2]
%\frametitle{Composition effects: Comparing with Hummels (2007) (cont')}
Five differences with our method  \vspace{0.1cm}
\footnotesize
\begin{enumerate}

\item Hummels (2007) obtains the fitted ad-valorem rate in one step (the LHS is the observed price gap) while we use a 2-step approach (extract the fitted TC from the \textit{estimated} unfitted ad-valorem rate) - but a slight difference \vspace{0.1cm}
\item Hummels (2007) does not purge its measure of the fitted ad-valorem rate by the country-sector fixed effect  - but only a scale effect \vspace{0.1cm}
\item We separate the country-product fixed effects in two components (country / product), due to the number of fixed effects to estimate in the non-linear setting - robustness analysis to this point (in progress) \vspace{0.1cm}
\item We differ in the weighting scheme to obtain the yearly value of the fitted TC measure.  \vspace{0.1cm}
\begin{itemize}
\footnotesize
\item[-] Hummels (2007): The unweighed average value over the $i,k$ dimension \vspace{0.1cm}
\item[$\neq$] We weight each flow by its relative value in total trade flows observed in 1974 \vspace{0.1cm}
\item[-] Not much of a difference provided the weighting scheme in value is constant over time \vspace{0.1cm}
\item[-] Results robust to the alternative weighting scheme (apply Hummels's (2007) method) \hyperlink{app_compeffects_Hummels_rob}{\beamergotobutton{See}}
\end{itemize}

@@

\begin{frame}[label = app_compeffects_Hummels_rob]
\textbf{Excluding the composition effects: Robustness check}
\begin{itemize}
\item Applying Hummel's (2007) weighting scheme rather than ours \hyperlink{slide_compeffects_figure}{\beamergotobutton{Compare}}
\begin{itemize}
\item[-] Take the unweighed average value over the $i,k$ dimension to get the fitted $TC$ measure
\end{itemize}
\end{itemize}
\begin{figure}[htbp]
%\caption{Transport costs (with and without composition effects)}
%\label{fig:totalTC_compeffects_excl}
\begin{center}
\includegraphics[height=6cm]
{graph_composition_all_np.pdf}
\end{center}
\end{figure}

\hyperlink{app_compeffects_Hummels2}{\beamergotobutton{Back to slide}}
\end{frame}
